Stimjim is open source hardware for precise electrical stimulation

### 2019-05-28 benchmarking/paper/draft2.Rnw
realized my 5k resistors were actually 5.05k. modified gain multiplier in library and schematic (kicad and pdf) to say 5.05k.

projectDirectory = '/home/x/Desktop/stimjim/benchmarking/'
setwd(projectDirectory)

@@

    sh.median = median(x[which(isStageHigh>0)])*vpau
    sh.sd = sd(x[which(mmand::erode(isStageHigh, rep(1,13))>0)])*vpau
    sl.median = median(x[which(isStageLow>0)])*vpau
    sl.sd = sd(x[which(mmand::erode(isStageLow, rep(1,13))>0)])*vpau

@@

y = ex4[163:220,2]
x=1:length(y)/2
plot(x,y)
mod = nls(y~a*(1-exp(-x/t))+b, start=list(a=-10,t=10,b=5))
lines(x,predict(mod))
@

>>>>

projectDirectory = '/home/x/Dropbox (Technion Dropbox)/stimjim/benchmarking/'
setwd(projectDirectory)

@@

    ishe = which(mmand::erode(isStageHigh>0, rep(1,31)) > 0)
    isle = which(mmand::erode(isStageLow>0, rep(1,31)) > 0 )
    sh.median = median(x[ishe])*vpau
    sh.sd = sd(x[ishe])*vpau
    sl.median = median(x[isle])*vpau
    sl.sd = sd(x[isle])*vpau

@@

#y = ex4[163:220,2]
#x=1:length(y)/2
#plot(x,y)
#mod = nls(y~a*(1-exp(-x/t))+b, start=list(a=-10,t=10,b=5))
#lines(x,predict(mod))
@
